Descriptives for potential paper 1 

### 2022-08-13 Descriptives_potential_paper_1_20220622.Rmd
Add files via upload

#lm
fascicle_age_gam <- lapply(fascicle_names, function(x) 
{
  gam(substitute(i ~ s(PAT_AGE_AT_EXAM), list(i = as.name(x))), data = df_unique_empi)
})
names(fascicle_age_gam) <- fascicle_names

@@

>>>>

#lm
fascicle_age_gam <- lapply(fascicle_names, function(x) 
{
  gam(substitute(i ~ s(PAT_AGE_AT_EXAM, k=4), list(i = as.name(x))), data = df_unique_empi)
})
names(fascicle_age_gam) <- fascicle_names

@@

visreg(fascicle_age_gam$FAT_L)
```
